<header style="text-align: center">

### 2019-05-21 report/report.Rmd
Fix report sections organization
Add animation function and gif to report

@@

@@

## Air Traffic Evolution {.tabset .tabset-fade}

@@

@@

>>>>

## Air Traffic Evolution

@@

## Diverted Flights {.tabset .tabset-fade}

@@

@@

### Animation {-}

```{r, message=FALSE, results=FALSE}
gifname <- 'diverted'
giffile <- file.path('..', 'data', paste0(gifname, '.gif'))
if (!file.exists(giffile)) {
	ddr.animate(data$real$routes[id %in% div[, id]], giffile)
}
```
![Diverted Flights Map Animation](`r giffile`) \

@@

- Statistics (mean + sigma) for delays on each airport per day
